Automated Topic Naming

### 2011-09-06 ese/ese.tex
added dates

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management Systems (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent dirichlet allocation \and Topic models}

@@

%migod
While machine learning techniques can automatically identify clumps of
commonly recurring terms, devising an appropriate summary label for
each clump/topic is harder.  
A given topic extracted from a set of commit logs might consist of the following terms: \emph{ ``listener change remove add fire''}. 
This topic might reasonably be labelled as
``\emph{event handling}'' by a developer who understands the domain well,
despite the fact that this label does not appear in the word list itself.  
Current approaches to topic labelling rely on manual intervention by
human experts, and also are limited to project-specific topic labels.  
In this paper, we introduce \emph{labelled topic extraction}, an
approach to topic labelling that creates labels automatically that are
project independent.
%is both automatic and creates labels that are project independent.

@@

Similarly, Mockus and Votta~\cite{Mockus00} study a large-scale industrial change-tracking system. 
Mockus and Votta leverage WordNet~\cite{Fellbaum1998}, an English-language ``lexical database'' that contains semantic relations between words,
including common related forms (similar to word stemming), meronymy and synonymy.
They use WordNet for word roots as they felt the synonyms would be
non-specific and cause errors.
%, problems we also encountered. 
Mockus et al. validate their labels with system developers.
Since we study multiple projects, instead of a single project, these
kind of interviews are not feasible (particularly in the distributed world of open-source software).

Another approach is to extract concerns from software repositories.
Marcus et al.~\cite{marcus04wcre} use Latent Semantic Indexing (LSI)
to identify commonly occurring concerns for software maintenance. 
The
concerns are given by the user, and LSI is used to retrieve them from
a corpus. 
Topic modelling generates topics that are independent of a user query, and relate only to word frequencies in the corpus.
%Some results were interesting, but their precision was quite low. 
With ConcernLines, Treude et al.~\cite{treude09cl} show tag occurrence
using colour and intensity. 
They mine
developer created tags 
%change request tags (such as `milestone 3') and used these 
in order to analyze the evolution of a single product.
% make evolutionary analyses of a single product. 
The presence of a well-maintained set of tags is obviously essential to the success of this technique.

@@

% in our previous work~\cite{Hindle09ICSM}, as well as -- CITED a little too often (vanity cites!)
In Baldi et al.~\cite{Baldi2008}, topics are named manually: human
experts read the highest-frequency members of a topic and assign a
label accordingly. 
%XXX Possible to cut this
As discussed earlier, given the topic \emph{``listener change remove add fire''}, Baldi et al. would assign the label \emph{event-handling}. 
The labels are reasonable enough, but still require an expert in the field to determine them. 
Furthermore, these labels are project-specific, because they are generated from the data of that project. E.g., we might have a label called \emph{`Oracle'}
in the MySQL case, since Oracle owns MySQL. 
%We do this differently.
%This paper does this differently. 
Our approach differs: first of all, we automate the process of naming the topics; secondly, we label topics with project-independent terms, in order
to permit cross-project comparison.

@@

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, to control for differences in functional, rather than non-functional, requirements. 
We used three different open-source, partially-commercial database systems:
\begin{itemize}
\item  MySQL 3.23. Started in 1994 and MySQL 3.23 was released in early 2001. MySQL contains $320,000$ lines of C and C++ source code\footnote{generated
using David A. Wheeler's \emph{SLOCCount}, {http://dwheeler.com/sloccount}.}.
\item MaxDB 7.500. Started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project
has over $940,000$ lines of C source code. 
\item PostgreSQL 7.3. Started in the 1980s as a Berkeley research project. PostgreSQL 7.3 contains $306,000$ lines of C code.
\end{itemize}

>>>>

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management System (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent dirichlet allocation \and Topic models}

@@

%migod
While machine learning techniques can automatically identify clumps of
commonly recurring terms, devising an appropriate summary label for
each clump/topic is harder.  
A given topic extracted from a set of commit logs might consist of the following terms: \emph{ ``listener change remove add fire''}. 
This topic might reasonably be labelled as
\emph{``event handling''} by a developer who understands the domain well,
despite the fact that this label does not appear in the word list itself.  
Current approaches to topic labelling rely on manual intervention by
human experts, and also are limited to project-specific topic labels.  
In this paper, we introduce \emph{labelled topic extraction}, an
approach to topic labelling that labels topics automatically with
labels that are project independent.
%is both automatic and creates labels that are project independent.

@@

Similarly, Mockus and Votta~\cite{Mockus00} studied a large-scale industrial change-tracking system. 
Mockus and Votta leveraged WordNet~\cite{Fellbaum1998}, an English-language ``lexical database'' that contains semantic relations between words,
including common related forms (similar to word stemming), meronymy and synonymy.
They used WordNet for word roots as they felt the synonyms would be
non-specific and cause errors.
%, problems we also encountered. 
Mockus et al. validated their labels with system developers.
Since we study multiple projects, instead of a single project, these
kind of interviews were not feasible (particularly in the distributed world of open-source software).

Another approach is to extract concerns from software repositories.
Marcus et al.~\cite{marcus04wcre} used Latent Semantic Indexing (LSI)
to identify commonly occurring concerns for software maintenance. 
The
concerns are given by the user, and LSI is used to retrieve them from
a corpus. 
Topic modelling generates topics that are independent of a user query, and relate only to word frequencies in the corpus.
%Some results were interesting, but their precision was quite low. 
With ConcernLines, Treude et al.~\cite{treude09cl} showed tag occurrence
using colour and intensity. 
They mined
developer created tags 
%change request tags (such as `milestone 3') and used these 
in order to analyze the evolution of a single product.
% make evolutionary analyses of a single product. 
The presence of a well-maintained set of tags is obviously essential to the success of this technique.

@@

% in our previous work~\cite{Hindle09ICSM}, as well as -- CITED a little too often (vanity cites!)
In Baldi et al.~\cite{Baldi2008}, topics are named manually: human
experts read the highest-frequency members of a topic and assign a
label accordingly. 
%XXX Possible to cut this
As discussed earlier, given the topic \emph{``listener change remove add fire''}, Baldi et al. would assign the label \emph{event-handling}. 
The labels are reasonable enough, but still require an expert in the field to determine them. 
Furthermore, these labels are project-specific, because they are
generated from the data of that project. For example we might have a label called \emph{`Oracle'}
in the MySQL case, since Oracle owns MySQL. 
%We do this differently.
%This paper does this differently. 
Our approach differs: first of all, we automate the process of naming the topics; secondly, we label topics with project-independent terms, in order
to permit cross-project comparison.

@@

To evaluate our approach, we sought candidate systems that were mature projects and had openly accessible source control repositories. 
We selected systems from the same application domain, to control for differences in functional, rather than non-functional, requirements. 
We used three different open-source, partially-commercial database systems:
\begin{itemize}
\item  MySQL 3.23. Started in 1994 and MySQL 3.23 was released in early 2001. MySQL contains $320,000$ lines of C and C++ source code~\footnote{generated
using David A. Wheeler's \emph{SLOCCount},
{http://dwheeler.com/sloccount}.}. We used MySQL 3.23 history from July
31st, 2000 to August 9th 2004.
\item MaxDB 7.500. Started in the late 1970s as a research project, and was later acquired by SAP. As of version 7.500, released April 2007, the project
has over $940,000$ lines of C source
code~\footnote{{http://www.sdn.sap.com/irj/sdn/maxdb}}. 
 We used MaxDB 7.500 history from June
29th, 2004 to June 19th 2006.
\item PostgreSQL 7.3. Started in the 1980s as a Berkeley research
  project~\footnote{{http://www.postgresql.org/docs/7.3/static/}}. PostgreSQL
  7.3 contains $306,000$ lines of C code.
 We used PostgreSQL 7.3 history from May 9th, 2002 to 
 August 26th 2004.
